---
title: "results to comment"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Results of proportions

Of the total of 19600 triplet combinations, we could calculate structural niche and fitness differences for 18674. 

The number of coexisting triplets is 2562 (proportion of 0.1371961) (object "coex_triplets")

The number of non-coexisting triplets is 16112 (proportion of 0.8628039) (object "non_coex_triplets")

Of those coexisting triplets 

The number of triplets that coexist when also all three species pairs coexist is 260 (proportion of 260/2562=0.1014832) (object "all_coex_pairs") 

The number of triplets that coexist when at least some pairs but not all coexist is 2044 (diffuse competition) (proprotion of 2044/2562=0.7978142) (object "diffuse")

The number of triplets that coexist when no pair coexist is (intransitivity) 258
(proportion of 260/2562=0.1007026) (object "intransitivity") 




```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
